### 2019-11-19 paper/introduction.tex
minor important changes

The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) 2,250
MW$_{th}$ was introduced by the Chinese Academy of Sciences \cite{li_optimization_2018}. The
SD-TMSR
is a graphite-moderated thermal-spectrum \gls{MSR} operating in Th/$^{233}$U
fuel cycle. In the SD-TMSR, the fissile and fertile elements are integrated
into a single salt. To improve the breeding ratio, the active core is divided into two zones:
the radius of the fuel channels in the outer zone is modified to be larger
than the radius of the fuel channels in the inner zone \cite{nuttin2005potential,li_optimization_2018}.

Historically, the thermal-spectrum \gls{MSR} was designed for the Th/$^{233}$U
fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,
	merle2004scenarios,rosenthal1970molten}. This design assumes that we have
fissile $^{233}$U inventory to start up new \glspl{MSR}. However, $^{233}$U does not
exist in the Earth's crust and can only be produced from fertile $^{232}$Th in 
specific nuclear facilities. Therefore, we examine alternative fissile
materials to replace the $^{233}$U in the startup fuel
composition \cite{betzler2016modeling,zou2018transition}. The thorium fuel
cycle transition can be achieved after reaching the doubling
time $-$ time required to produce enough amount of $^{233}$U to trigger a
	new SD-TMSR $-$ of $^{233}$U because in this case, all startup fissile material
is being substituted by newly produced $^{233}$U.

@@

Heuer \emph{et al.} (2014) discussed the transition characteristics of the \gls{MSFR}
under different launching scenarios (e.g., enriched uranium and TRU); they concluded that starting the thorium fuel cycle is feasible in the MSFR while closing the current fuel cycle and optimizing the management of the long-term wastes. \cite{heuer2014towards}.

Various previous works explore starting the
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many such publications have focused on the fast-spectrum \glspl{MSR} \cite{heuer2014towards,ashraf2019modeling,
	ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
	fiorina2013investigation}, while few focus on
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling,
	zou2018transition,zou2018preliminary}. For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other
fissile materials (except $^{233}$U) has not been studied before. Therefore,
the main objective of the present paper is to establish feasible strategies for thorium fuel cycle transition in the \gls{SD-TMSR} with
various initial fissile materials and without any external feed of $^{233}$U. We investigate five different
initial fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU} from LWR SNF, and $^{233}$U \cite{de2000scenarios}. Two different feed mechanisms were selected:

\begin{itemize}
	\item Thorium feed mechanism: continuous feed flow of thorium from the thorium stockpile and $^{233}$U from the \texttt{Pa-decay tank}\footnote{An external tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. \cite{betzler2016modeling}.
	\item Non-thorium feed mechanism: continuous injection of the same initial heavy metals (excluding Th) and simultaneous feed of all or fraction of $^{233}$U from the \texttt{Pa-decay tank}.
\end{itemize}

All calculations presented in this paper are performed using SERPENT-2 version 2.1.31 \cite{leppanen2014serpent}. We use the MSR burnup routine provided by SERPENT-2 to simulate continuous online reprocessing and refueling. SERPENT-2 uses an internal calculation routine for solving the Bateman equations describing the changes in the material compositions caused by neutron-induced reactions and radioactive decay \cite{leppanen2014serpent}. Additionally, SERPENT-2 enables burnup calculations on computer clusters with multiple cores using distributed-memory MPI parallelization.

This paper is organized as follows: section \ref{Introduction} introduces \gls{MSR} systems, section \ref{Model-description} discusses the model description, section \ref{Methodology-and-tools} describes methodology and tools, section \ref{Feed-and-extraction-rates} addresses extraction and feed mechanisms, section \ref{Results-and-discussion} focuses on the results and discussion, and section \ref{Conclusion} highlights the conclusions.

>>>>

The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with a thermal power of 2,250
MW$_{th}$ was introduced by the Chinese Academy of Sciences \cite{li_optimization_2018}. The
SD-TMSR
is a graphite-moderated thermal-spectrum \gls{MSR} operating in Th/$^{233}$U
fuel cycle. In the SD-TMSR, the fissile and fertile elements are integrated
into a single salt. To improve the breeding ratio, the active core is divided into two zones:
the radius of the fuel channels in the outer zone is modified to be larger
than the radius of the fuel channels in the inner zone \cite{nuttin2005potential,li_optimization_2018}.

Historically, the thermal-spectrum \gls{MSR} was designed for the Th/$^{233}$U
fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,
	merle2004scenarios,rosenthal1970molten}. This design assumes that we have
fissile $^{233}$U inventory to start up new \glspl{MSR}. However, $^{233}$U does not
exist in the Earth's crust and can only be produced from fertile $^{232}$Th in 
specific nuclear facilities. Therefore, we examine alternative fissile
materials to replace the $^{233}$U in the startup fuel
composition \cite{betzler2016modeling,zou2018transition}. The thorium fuel
cycle transition can be achieved after reaching the doubling
time of $^{233}$U $-$ time required to produce enough amount of $^{233}$U to trigger a
	new SD-TMSR $-$ because in this case, all startup fissile material
is being substituted by newly produced $^{233}$U.

@@

Heuer \emph{et al.} (2014) discussed the transition characteristics of the \gls{MSFR}
under different launching scenarios (e.g., enriched uranium and TRU); they concluded that starting the thorium fuel cycle is feasible in the MSFR while closing the current fuel cycle and optimizing the management of the long-term wastes \cite{heuer2014towards}.

Various previous works explore starting the
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many such publications have focused on the fast-spectrum \glspl{MSR} \cite{heuer2014towards,ashraf2019modeling,
	ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
	fiorina2013investigation}, while few focus on
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling,
	zou2018transition,zou2018preliminary}. For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other
fissile materials (except $^{233}$U) has not been studied before. Therefore,
the main objective of the present paper is to establish feasible strategies for thorium fuel cycle transition in the \gls{SD-TMSR} with
various initial fissile materials and without any external feed of $^{233}$U. We investigate five different
initial fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu \cite{marka1993explosive}, \gls{TRU} from LWR SNF \cite{de2000scenarios}, and $^{233}$U. Two different feed mechanisms were selected:

\begin{itemize}
	\item \textbf{Thorium feed mechanism}: continuous feed flow of thorium from the external stockpile and $^{233}$U from the \texttt{Pa-decay tank}\footnote{An external tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U \cite{betzler2016modeling}.
	\item \textbf{Non-thorium feed mechanism}: continuous injection of external heavy metals (\gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}) and simultaneous feed of all or fraction of $^{233}$U from the \texttt{Pa-decay tank}.
\end{itemize}

All calculations presented in this paper are performed using SERPENT-2 version 2.1.31\footnote{SERPENT-2 is a 3D continuous energy Monte Carlo neutron 
	transport and burnup code.} \cite{leppanen2014serpent}. We use the MSR burnup routine provided by SERPENT-2 to simulate continuous online reprocessing and refueling. SERPENT-2 uses an internal calculation routine for solving the Bateman equations describing the changes in the material compositions caused by neutron-induced reactions and radioactive decay \cite{leppanen2014serpent}. Additionally, SERPENT-2 enables burnup calculations on computer clusters with multiple cores using distributed-memory MPI parallelization.

This paper is organized as follows: section \ref{Model-description} discusses the model description, section \ref{Methodology-and-tools} describes methodology and tools, section \ref{Feed-and-extraction-rates} addresses extraction and feed mechanisms, section \ref{Results-and-discussion} focuses on the results and discussion, and section \ref{Conclusion} highlights the conclusions.

### 2019-11-19 paper/methods.tex
minor important changes

\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.png}
	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
	SD-TMSR \cite{ashraf2019Preliminary}.}
	\label{fig:ff}
\end{figure}

@@

\subsection{Fuel composition}
The general composition of the liquid fuel salt in this work is 70LiF - 
17.5BeF$_2$ - 12.5(HM)F$_N$ mole\%, where HM is the heavy metal (mixture of 
thorium and one of these fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU} from LWR SNF, and $^{233}$U).
The aim of this paper is to simulate the  
operation of the \gls{SD-TMSR} for 60 years with various startup fissile 
compositions and without any external feed of fissile $^{233}$U which we 
assume is unavailable. For that reason, five different types of initial 
fissile materials are considered based on \gls{HALEU}, Pu, and \gls{TRU} from Light Water
Reactor (LWR) spent nuclear fuel (SNF):
\begin{enumerate}[label=(\alph*)]
	\item High Assay Low Enriched Uranium (HALEU) (19.79\%),
	\item Pu mixed with \gls{HALEU} (19.79\%),
	\item reactor-grade Pu \cite{marka1993explosive},
	\item transuranic (TRU) elements from LWR SNF \cite{de2000scenarios}, and
	\item $^{233}$U for comparison \cite{ashraf2019whole_core}.
\end{enumerate}
All types of initial fissile materials are fed as fluorides.
The reactor-grade Pu and \gls{TRU} compositions are summarized in 
Table~\ref{tab:table2} and ~\ref{tab:table3}, respectively.

@@

For the reactor-grade Pu case, the composition is taken for Pu 
recovered from the SNF composition of a commercial \gls{PWR} with an 
average discharge burnup of $33$ $GWd/tHM$ and after $10$ years of cooling before 
reprocessing \cite{oecd1989probabilistic,marka1993explosive}. Similarly, the 
isotopic compositions of \gls{TRU} reflect the composition of the \gls{PWR} UOX SNF 
(after one use, no multi-recycling) with an average discharge of $60$ 
$GWd/tHM$ burnup and after $5$ years of cooling \cite{de2000scenarios}. 
The molar composition of startup fuel for all five cases is listed in 
Table~\ref{tab:table4}. Additionally, the corresponding initial nuclei 
inventories with various fissile fuel options are summarized in 
Table~\ref{tab:table5}.
\begin{table}  %[!ht]
	\caption{Molar composition for startup fuel salts (mole\%).}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.13\textwidth} X p{0.18\textwidth} 
	p{0.14\textwidth} X X}
		\hline
		Fuel salt component& \gls{LEU} (19.79 wt.\%) & Pu+enriched U (19.79 wt.\%) 
		&  reactor-grade Pu & \gls{TRU}& $^{233}$U \\
		\hline
		LiF&70.0&70.0&70.0&70.0&70.0\\
		BeF$_2$&17.5&17.5&17.5&17.5&17.5\\
		ThF$_4$&8.25&7.50&10.75&	8.65&12.3		\\
		UF$_4$&4.25&4.75&&&	0.20		\\
		PuF$_3$&&0.25&1.75&&		\\
		(TRU)F$_3$&&&	&3.85	&\\
		\hline
	\end{tabularx}
	\label{tab:table4}
\end{table}

\begin{table}  %[!ht]
	\caption{Initial heavy metal inventories for 
	various initial fissile loadings (kg).}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{X X p{0.18\textwidth} 
	p{0.14\textwidth} X X}
		\hline
		Nuclide & \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) &  
		reactor-grade Pu & \gls{TRU}& $^{233}$U \\	\hline
		$^{232}$Th       &6.24E+04 & 4.67E+04 &   6.75E+04			& 5.44E+04	& 7.69E+04    \\ 
		$^{233}$U        &         & &        &       &  1.30E+06 \\
		$^{235}$U        & 3.17E+03 &6.01E+03	&            &   & \\
		$^{238}$U      	 &1.28E+04  &2.43E+04 &	&  &\\
		$^{237}$Np	  	 &         && &1.58E+03	&    \\
		$^{238}$Pu	  	 &         &1.60E+01	& 1.13E+02 & 6.78E+02	&   \\
		$^{239}$Pu       &         &9.59E+02&6.76E+03& 1.15E+04&    \\
		$^{240}$Pu       &         &3.99E+02& 2.82E+03&5.40E+03&  	\\  
		$^{241}$Pu		 &         &1.60E+02&1.13E+03&2.69E+03&   \\
		$^{242}$Pu		 &         &6.39E+01	&4.51E+02	& 1.68E+03& \\
		$^{241}$Am		 &         &&& 8.53E+02 & \\
		$^{242}$Am		 &         &&&  &\\
		$^{243}$Am       &        & &&4.77E+02&\\
		$^{244}$Cm		 &        & &&2.01E+02&  \\
		$^{245}$Cm		 &        & &&			2.51E+01	&   \\ 
		\hline
	\end{tabularx}
\label{tab:table5}
\end{table}

@@

Simulation of liquid-fueled Molten Salt Reactor (MSR) systems requires 
computational software that can support online fuel salt reprocessing and 
refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 
\footnote{SERPENT-2 is a 3D continuous energy Monte Carlo neutron 
transport and burnup code.} \cite{leppanen2014serpent} simulates the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) full-core with various initial fuel types. This extension 
of SERPENT accounts for continuous online reprocessing and refueling 
\cite{aufiero2013extended}. The ENDF-VII.0 cross section library was used for all 
calculations in this work. The results demonstrate full-core runs of 
$1.25\times 10^7$ neutron histories per depletion step. The full burnup time of 
the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ 
$12$ $pcm$. The online extraction of \gls{FPs} and other neutron absorbers 
provides many benefits for MSRs. For example, it has the potential to reduce the initial 
fissile material inventory required to achieve criticality and improve the 
breeding ratio. Figure~\ref{fig:flow} shows a flow chart of the calculation 
steps.

@@

As shown in Figure~\ref{fig:flow}, after launching the input file, SERPENT solves the Bateman equation using an advanced 
matrix exponential solution based on the Chebyshev Rational Approximation 
Method \cite{isotalo2016improving}. 
Then, the system extracts gaseous \gls{FPs} and other materials 
(non-dissolved metals, lanthanides, and soluble metals except Pa) with 
a suitable removal rate\footnote{The extraction rate depends on the type of 
poison and its impact on the neutron
economy.}. This is done by setting the 
flow rate of gaseous \gls{FPs} and other materials from the fuel to the 
\texttt{FP-waste tank}\footnote{An external tank used to store the gaseous 
\gls{FPs} and the other materials (non-dissolved metals, lanthanides, and 
soluble metals except protactinium).}. Specifically, Pa is removed 
from the fuel with a certain flow rate into the 
\texttt{Pa-decay tank} to decay and produce $^{233}$U\footnote{The 
$^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ 
$\approx$ $27$ $d$.}. The produced $^{233}$U is used as a fresh fissile fuel 
and the residual $^{233}$U (if exist) is the net production of $^{233}$U that required to start up a new SD-TMSR and achieve the transition to thorium fuel cycle. The MSR burnup 
routine provided by SERPENT-2 allows changes to the mass flow rates ($mflow$) of the 
isotopes during reactor operation \cite{aufiero2013extended}. Specifically, the SERPENT user should determine the mass flow rate ($mflow$), which is the rate by 
which elements or nuclides are transferred between materials. After that, the 
flow rates must be connected to materials with a reprocessing scheme. 
The final step is to link the reprocessing schemes to depletion histories. In 
the present work, we adjust the transfer rates of fresh fuel to maintain core 
criticality and to keep fuel salt mass constant during burnup. The continuous feed constant calculation procedures are summarized as follows:
\begin{enumerate}
	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-tank}, respectively.
	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
	\subitem 3a. \textbf{Thorium feed mechanism}: mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
	\subitem 3b. \textbf{Non-thorium feed mechanism}: mass of the heavy metals (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant.
\end{enumerate}
The cycle calculation runs iteratively until the burnup reaches the desired worth.

\section{Feed and extraction rates} \label{Feed-and-extraction-rates}
In the present work, two different feed mechanisms are used: (1) thorium and (2) non-thorium.
The first mechanism allows continuous feed flow of thorium from the thorium stockpile and 
$^{233}$U from the \texttt{Pa-decay tank}. In contrast, the second mechanism 
continuously injects heavy metal (HM) (excluding Th) and simultaneously feeds  
all or part of produced $^{233}$U from the \texttt{Pa-decay tank}. The fission 
products (FPs) act as poisons in MSRs: they negatively impact the reactivity. 
Therefore, \gls{FPs} must be extracted during reactor operation. Consider 
$T_{r}$ as the time during which the total fuel salt is reprocessed and 
$dN_{e}$ as the amount of particular element $e$ with inventory $N_{e}$ that 
the \gls{MSR} extracts during time $dt$, thus \cite{nuttin2005potential}

>>>>

\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.png}
	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
	SD-TMSR.}
	\label{fig:ff}
\end{figure}

@@

\subsection{Fuel composition}
The general composition of the startup liquid fuel salt in this work is 70LiF - 
17.5BeF$_2$ - 12.5(HM)F$_N$ mole\%, where HM is the heavy metal (mixture of 
thorium and one of these fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}, and $^{233}$U).
The aim of this paper is to simulate the  
operation of the \gls{SD-TMSR} for 60 years with various startup fissile 
compositions and without any external feed of fissile $^{233}$U which we 
assume is unavailable. For that reason, five different types of initial 
fissile materials are considered based on \gls{HALEU}, Pu, and \gls{TRU} from Light Water
Reactor (LWR) spent nuclear fuel (SNF):
\begin{enumerate}[label=(\alph*)]
	\item High Assay Low Enriched Uranium (HALEU) (19.79\%),
	\item Pu mixed with \gls{HALEU} (19.79\%),
	\item reactor-grade Pu \cite{marka1993explosive},
	\item transuranic (TRU) elements from LWR SNF \cite{de2000scenarios}, and
	\item $^{233}$U for comparison \cite{ashraf2019whole_core}.
\end{enumerate}
All types of initial fissile materials are fed as fluorides.
The reactor-grade Pu and \gls{TRU} compositions are summarized in 
Table~\ref{tab:table2} and ~\ref{tab:table3}, respectively.

@@

For the reactor-grade Pu case, the composition is taken for Pu 
recovered from the SNF composition of a commercial \gls{PWR} with an 
average discharge burnup of $33$ $GWd/tHM$ and after $10$ years of cooling before 
reprocessing \cite{oecd1989probabilistic,marka1993explosive}. Similarly, the 
isotopic compositions of \gls{TRU} reflect the composition of the \gls{PWR} UOX SNF 
(after one use, no multi-recycling) with an average discharge of $60$ 
$GWd/tHM$ burnup and after $5$ years of cooling \cite{de2000scenarios}. 
The molar composition of startup fuel for all five cases is listed in 
Table~\ref{tab:table4}. Additionally, the corresponding initial nuclei 
inventories with various fissile fuel options are summarized in 
Table~\ref{tab:table5}.
\begin{table}  %[!ht]
	\caption{Molar composition for startup fuel salts (mole\%).}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.13\textwidth} X p{0.18\textwidth} 
	p{0.14\textwidth} X X}
		\hline
		Fuel salt component& \gls{HALEU} (19.79 wt.\%) & Pu+\gls{HALEU} (19.79 wt.\%) 
		&  reactor-grade Pu & \gls{TRU}& $^{233}$U \\
		\hline
		LiF&70.0&70.0&70.0&70.0&70.0\\
		BeF$_2$&17.5&17.5&17.5&17.5&17.5\\
		ThF$_4$&8.25&7.50&10.75&	8.65&12.3		\\
		UF$_4$&4.25&4.75&&&	0.20		\\
		PuF$_3$&&0.25&1.75&&		\\
		(TRU)F$_3$&&&	&3.85	&\\
		\hline
		Total HM &12.5&12.5&12.5&12.5&12.5\\
		\hline
	\end{tabularx}
	\label{tab:table4}
\end{table}

\begin{table}  %[!ht]
	\caption{Initial heavy metal inventories for 
	various initial fissile loadings (kg).}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{X X p{0.18\textwidth} 
	p{0.14\textwidth} X X}
		\hline
		Nuclide & \gls{HALEU} (19.79\%) & Pu+\gls{HALEU} (19.79wt.\%) &  
		reactor-grade Pu & \gls{TRU}& $^{233}$U \\	\hline
		$^{232}$Th       &6.24E+04 & 4.67E+04 &   6.75E+04			& 5.44E+04	& 7.69E+04    \\ 
		$^{233}$U        &         & &        &       &  1.30E+03 \\
		$^{235}$U        & 3.17E+03 &6.01E+03	&            &   & \\
		$^{238}$U      	 &1.28E+04  &2.43E+04 &	&  &\\
		$^{237}$Np	  	 &         && &1.58E+03	&    \\
		$^{238}$Pu	  	 &         &1.60E+01	& 1.13E+02 & 6.78E+02	&   \\
		$^{239}$Pu       &         &9.59E+02&6.76E+03& 1.15E+04&    \\
		$^{240}$Pu       &         &3.99E+02& 2.82E+03&5.40E+03&  	\\  
		$^{241}$Pu		 &         &1.60E+02&1.13E+03&2.69E+03&   \\
		$^{242}$Pu		 &         &6.39E+01	&4.51E+02	& 1.68E+03& \\
		$^{241}$Am		 &         &&& 8.53E+02 & \\
		$^{242}$Am		 &         &&&  &\\
		$^{243}$Am       &        & &&4.77E+02&\\
		$^{244}$Cm		 &        & &&2.01E+02&  \\
		$^{245}$Cm		 &        & &&			2.51E+01	&   \\ 
		\hline
	\end{tabularx}
\label{tab:table5}
\end{table}

@@

Simulation of liquid-fueled Molten Salt Reactor (MSR) systems requires 
computational software that can support online fuel salt reprocessing and 
refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 \cite{leppanen2014serpent} simulates the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) full-core with various initial fuel types. This extension 
of SERPENT accounts for continuous online reprocessing and refueling 
\cite{aufiero2013extended}. The ENDF-VII.0 cross section library was used for all 
calculations in this work. The results demonstrate full-core runs of 
$1.25\times 10^7$ neutron histories per depletion step. The full burnup time of 
the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ 
$12$ $pcm$. The online extraction of \gls{FPs} and other neutron absorbers 
provides many benefits for MSRs. For example, it has the potential to reduce the initial 
fissile material inventory required to achieve criticality and improve the 
breeding ratio. Figure~\ref{fig:flow} shows a flow chart of the calculation 
steps.

@@

As shown in Figure~\ref{fig:flow}, after launching the input file, SERPENT solves the Bateman equation using an advanced 
matrix exponential solution based on the Chebyshev Rational Approximation 
Method \cite{isotalo2016improving}. 
Then, the system extracts gaseous \gls{FPs} and other materials 
(non-dissolved metals, lanthanides, and soluble metals except Pa) with 
a suitable removal rate\footnote{The extraction rate depends on the type of 
poison and its impact on the neutron
economy.}. This is done by setting the 
flow rate of gaseous \gls{FPs} and other materials from the fuel to the 
\texttt{FP-waste tank}\footnote{An external tank used to store the gaseous 
\gls{FPs} and the other materials (non-dissolved metals, lanthanides, and 
soluble metals except protactinium).}. Specifically, Pa is removed 
from the fuel with a certain flow rate into the 
\texttt{Pa-decay tank} to decay and produce $^{233}$U\footnote{The 
$^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ 
$\approx$ $27$ $d$.}. The produced $^{233}$U is used as a fresh fissile fuel 
and the residual $^{233}$U (if exist) is the net production of $^{233}$U that required to start up a new SD-TMSR and achieve the transition to thorium fuel cycle. The MSR burnup 
routine provided by SERPENT-2 allows changes to the mass flow rates ($mflow$) of the 
isotopes during reactor operation \cite{aufiero2013extended}. Specifically, the SERPENT user should determine the mass flow rate ($mflow$), which is the rate by 
which elements or nuclides are transferred between materials. After that, the 
flow rates must be connected to materials with a reprocessing scheme. 
The final step is to link the reprocessing schemes to depletion histories. In 
the present work, we adjust the transfer rates of fresh fuel to maintain core 
criticality and to keep fuel salt mass constant during burnup. The continuous feed constant calculation procedures are summarized as follows:
\begin{enumerate}
	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-decay tank}, respectively.
	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
	\subitem 3a. \textbf{Thorium feed mechanism}: mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
	\subitem 3b. \textbf{Non-thorium feed mechanism}: mass of external heavy metals (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant.
\end{enumerate}
The cycle calculation runs iteratively until the burnup reaches the desired worth.

\section{Feed and extraction rates} \label{Feed-and-extraction-rates}
In the present work, two different feed mechanisms are used: (1) thorium and (2) non-thorium.
The first mechanism allows continuous feed flow of thorium from the external stockpile and 
$^{233}$U from the \texttt{Pa-decay tank}. In contrast, the second mechanism 
continuously injects external heavy metals (\gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}) and simultaneously feeds  
all or part of produced $^{233}$U from the \texttt{Pa-decay tank}. The fission 
products (FPs) act as poisons in MSRs: they negatively impact the reactivity. 
Therefore, \gls{FPs} must be extracted during reactor operation. Consider 
$T_{r}$ as the time during which the total fuel salt is reprocessed and 
$dN_{e}$ as the amount of particular element $e$ with inventory $N_{e}$ that 
the \gls{MSR} extracts during time $dt$, thus \cite{nuttin2005potential}
